\chapter*{List of Publications}
\pagestyle{plain}
%\chaptermark{ }
%\sectionmark{ }
%\addcontentsline{toc}{chapter}{List of Publications}

\newcounter{pubs_counter}

\begin{list}{[\arabic{pubs_counter}]~}{\usecounter{pubs_counter}}

\item
E.~Marchi, F.~Vesperini, S.~Squartini, and B.~Schuller, ``Deep recurrent neural network-based autoencoders for acoustic novelty detection,'' \emph{Computational Intelligence and Neuroscience}, 2016.

\item
F.~Vesperini, P.~Vecchiotti, E.~Principi, S.~Squartini, and F.~Piazza, ``Localizing speakers in multiple rooms by using deep neural,'' \emph{Computer Speech and Language}, 2017.

\item
F.~Vesperini, L.~Gabrielli, E.~Principi, and S.~Squartini,``Polyphonic sound event detection by using capsule neural networks,'' \emph{Journal of Selected Topics in Signal Processing}, 2018, submitted.

\item
E.~Marchi, F.~Vesperini, F.~Eyben, S.~Squartini, and B.~Schuller, ``A Novel Approach for Automatic Acoustic Novelty Detection Using a Denoising Autoencoder with Bidirectional LSTM Neural Networks,'' \emph{Proc. of ICASSP}, Brisbane, Australia, 19-24 Apr. 2015, IEEE.

\item
E.~Marchi, F.~Vesperini, F.~Weninger, F.~Eyben, S.~Squartini, and B.~Schuller, ``Non-Linear Prediction with LSTM Recurrent Neural Networks for Acoustic Novelty Detection,'' \emph{Proc. of IJCNN}, Killarney, Ireland, 12-16 Jul. 2015, IEEE.

\item
F.~Vesperini, P.~Vecchiotti, E.~Principi, S.~Squartini, and F.~Piazza, ``Deep neural networks for multi-room voice activity detection: Advancements and comparative evaluation,'' \emph{Proc. of IJCNN}, Vancouver, Canada, 24-29 Jul. 2016, IEEE, pp. 3391--3398.

\item
M.~Gasparini, F.~Vesperini, S.~Cecchi, S.~Squartini, F.~Piazza, and R.~Toppi, ``Combining evolution strategies and neural network procedures for compression driver design,'' \emph{Proc. of IJCNN}, Vancouver, Canada, 24-29 Jul. 2016, IEEE, pp. 3385--3390.

\item
P.~Vecchiotti, F.~Vesperini, E.~Principi, S.~Squartini, and F.~Piazza, ``Convolutional neural networks with 3-{D} kernels for voice activity detection in a multiroom environment,'' \emph{Multidisciplinary Approaches to Neural Computing}, pp. 161--170. Springer, 2018.

\item
F.~Vesperini, P.~Vecchiotti, E.~Principi, S.~Squartini, and F.~Piazza, ``A neural network based algorithm for speaker localization in a multi-room environment,'' \emph{Machine Learning for Signal Processing (MLSP), 2016 IEEE 26th International Workshop on}. IEEE, 2016, pp. 1--6.

\item
E.~Principi, F.~Vesperini, S.~Squartini, and F.~Piazza, ``Acoustic novelty detection with adversarial autoencoders,'' \emph{Proc. of IJCNN}, Anchorage, Alaska, 14-19 May 2017, IEEE, pp. 3324--3330.

\item
M.~Valenti, D.~Tonelli, F.~Vesperini, E.~Principi, and S.~Squartini, ``A neural network approach for sound event detection in real life audio,'' \emph{Proc. of EUSIPCO}, Kos, Greece, Sept. 2017, IEEE.

\item
L.~Gabrielli, C.~E. Cella, F.~Vesperini, D.~Droghini, E.~Principi, and S.~Squartini, ``Deep learning for timbre modification and transfer: An evaluation study,'' \emph{Proc. of 144th AES}, Milan, Italy, 24-26 May 2018, Audio Engineering Society.

\item
L.~Ambrosini, L.~Gabrielli, F.~Vesperini, S.~Squartini, and L.~Cattani, ``Deep neural networks for road surface roughness classification from acoustic signals,'' \emph{Proc. of 144th AES}, Milan, Italy, 24-26 May 2018, Audio Engineering Society.

\item
F.~Vesperini, A.~Galli, L.~Gabrielli, E.~Principi, and S.~Squartini, ``Snore sounds excitation localization by using scattering transform and deep neural networks,'' \emph{Proc. of IJCNN}, Rio de Janeiro, Brasil, 8-13 Jul. 2018, IEEE.

\item
F.~Vesperini, D.~Droghini, E.~Principi, L.~Gabrielli, and S.~Squartini, ``Hierarchic {C}onv{N}ets framework for rare sound event detection,'' \emph{Proc. of EUSIPCO}. IEEE, Sept. 3-7 2018.

\item
F.~Vesperini, L.~Romeo, E.~Principi, A.~Monteri\`{u}, and S.~Squartini, ``Convolutional recurrent neural networks and acoustic data augmentation for snore detection,'' \emph{Proc. of WIRN}, Vietri sul Mare, Italy, 13-15 Jun. 2018.

\item
D.~Droghini, F.~Vesperini, E.~Principi, S.~Squartini, and F.~Piazza, ``Few-shot siamese neural networks employing audio features for human-fall detection,'' \emph{Proc. of The International Conference on Pattern Recognition and Artificial Intelligence}, Union, NJ, USA, Aug. 15-17 2018.

  
\end{list}

\textbf{Others}:
\begin{list}{[\arabic{pubs_counter}]~}{\usecounter{pubs_counter}}
\item
F.~Vesperini, D.~Droghini, D.~Ferretti, E.~Principi, L.~Gabrielli, S.~Squartini, and F.~Piazza, ``A hierarchic multi-scaled approach for rare sound event detection,'' Ancona, Italy, 2017, {DCASE} {T}ech. {R}eport. {C}opyright-free.

\item 
F.~Vesperini, L.~Gabrielli, E.~Principi, and S.~Squartini, ``A capsule neural networks based approach for bird audio detection,'' Ancona, Italy, 2018, {DCASE} {T}ech. {R}eport. {C}opyright-free.

\item
L.~Gabrielli, F.~Vesperini, D.~Droghini, and S.~Squartini, ``Rima {G}lottidis: Experimenting generative raw audio synthesis for a sound installation,'' \emph{XXII Colloquium of Musical Informatics}, Udine, Italy, 20-23 Nov. 2018.

\end{list}
	



