\chapter{Background}\label{ch:backg}

The Computers are able to perform complex calculus operations in a short amount of time.
However computers cannot compete with humans in dealing with: common sense, ability to recognize people, objects, sounds, comprehension of natural language, ability to learn, categorize, generalize.

Therefore, why does the human brain show to be superior w.r.t common computers for these kind of problems?
Is there any chance to mimic the mechanisms characterizing the way of working of our brain in order to produce more efficient machines?

In the field of signal analysis, the aim is the characterization of such real-world signals in terms of \textit{signal models}, which can provide the basis for a theoretical description of a signal processing system. They are potentially capable of letting us learn a great deal about the signal source, without having to have the source available.

The ``Deep Learning'' is a new area of machine learningresearch, which has been introduced with the objective of movingMachine Learning closer to one of its original goals: Artificial Intelligence. Deep Learning is about learning multiple levels ofrepresentation and abstraction that help to make sense of datasuch as images, sound, and text.

Therefore, in this chapter a theoretical description of the principal Deep Neural Network (DNN) architectures is given. In addition, the algorithms used for their parameter estimation are described, with a focus on the most widely model structure used in the field of the computational acoustic event analysis.


\input{2_background/dnn}


